\vfill A Survey of Web Testing Frameworks and Workflow for Testing JavaScript Applications

### 2014-05-16 Paper/paper.tex
Testing frameworks edits, general spell-check

\subsection{Sample ToDo App}
In order to test out the various frameworks that we found online, we needed a small application with some functionality, but without the inherent complexity that was going to come with our evaluation application. After some searching, We decided upon a Todo application made with Express.js, Node.js, and MongoDB. \cite{ToDoAppHomePage} Here is a brief preview of the app:

@@

%%%%%%%%%%%%%%%%%%%%%%
%%% Testing Frameworks
%%%   Talk about the various frameworks
%%%%%%%%%%%%%%%%%%%%%%
\section{Testing Frameworks}

@@

JavaScript was chosen because it used in over 87\% of all websites. \cite{JSUsage}

@@

An important distinction that needs to be made is that in web applications there is functionality behind the scenes and there is the UI element of the web page. Unit testing frameworks

@@

This relates to Jasmine is the way that the developer writes Jasmine tests. The idea behind jasmine tests is that they read, as much as possible, like english sentences. As an example, the following is a valid Jasmine test:
\begin{lstlisting}
describe("Arithmetic Test", function () {
  it("should be able to compute the addition of two numbers", function () {
    expect(1 + 2).toEqual(3);
  });

@@

Asynchronous testing using Jasmine was a bit of a chore, but there is support built in. This support comes in the form of a three-set function progression. The first function, \lstinline!runs(function () { .... })!, runs the asynchronous code. The second function, \lstinline!waitsFor(function () { ... })!, polls a flag that is set by the first function when it completes. Finally, the third function, another \lstinline{runs(...)}, houses the assertions to determine if the code ran properly or not. This method requires a fairly substantial amount of typing as well as complicated function chains when more than one asynchronous call is required.

@@

Mocha, by default, also uses the \lstinline{describe -> it(\"should...\"} pattern to create tests. Mocha offers a variety of other test interfaces for developer's to write their test code the way they want to in addition to a custom, nearly unstructured variety. A few of the testing interfaces are outlined here:
\begin{lstlisting}
// BDD (default)
describe('BDD Suite', function () {
  it('should be test 1', function () {
    ...
  });
});

@@

Mocha's approach to asynchronous testing is quite a bit more straightforward than Jasmine's. In the \lstinline{it(...)} anonymous function, there is passed an additional parameter called \lstinline{done} which is then called when the asynchronous call has finished. This required us to edit the code we were testing to make all the async calls accept an additional callback, but it was a very small price to pay for extended testability. An example asynchronous test would look like this:
\begin{lstlisting}
describe("Asynch Mocha Test", function () {
  it("look like this", function (done) {
    myAsyncCall(param1, param2, function () {
      // This callback expected to run when async returns

@@

Overall Mocha offered more flexibilty and better asynchronous support at the cost of additional setup. This increased flexibility came in the way of being able to select our own assertion library so that our tests looked the way we wanted them. The cost of that was the need to find our own assertion library among the dozen that are out there. We prefer Mocha's method of asynchronous testing because it required considerably less typing on our part and was more easy to follow and read than a chain of method calls.

\paragraph{Assertion Library of Choice: Chai.js \cite{Chaijs}}
For the assertion library we chose Chai.js.  It offers the most flexibility for writing assertions that we'd found. It provides access to an Expect API, a Should API, and a more general Assert API. The Expect API provides assertions in the form of \lstinline{expect(myVar).to.equal(10);} or \lstinline{expect(myArr).to.have.length(10);}. The Should API has assertions of the form \lstinline{myVar.should.be.a(\'number\');} or \lstinline{myArr.should.have.length(10);}. Finally, the Assert API has the more tried and true \lstinline{assert.equal(myVar, 10);} and \lstinline{assert.lengthOf(myArr, 10);}. The various APIs combined with Mocha's flexibilty led to a nice developer experience that can appeal to a variety of different developers.

@@

\subsubsection{Intern\cite{InternIO}}
Intern is a hybrid unit testing and browser testing framework that aims to be an all-in-one testing framework. Intern has unit testing, browser testing, and code coverage information all built into the same tool. Intern runs on its own server which give it access to the internals of the project, but caused problems when attempting to interact with a seperate server running the Node.js application. We were unable to get the browser testing portion of Intern to work because of the inability to set up cross-server communication easily and properly.

%-AMD
Intern uses Asynchronous Module Definition (AMD) form which is something we'd not seen before. Where this comes into play is merely in what used to be \lstinline{require(...)}. Instead of seperately requiring modules, the entire program is wrapped in a \lstinline{define([...])} block that passes modules as parameters to an overarching function. That will make more sense after an example:
\begin{lstlisting}
// Intern
define([
    'intern!object',
    'intern/chai!assert',
    'app/hello'
], function (registerSuite, assert, hello) {
  // Test code here
});

@@

Using either style you get access to the modules outlined. AMD form offers a tighter, more straightforward way to look at module loading in addtiion to being better supported and having fewer gotchas. \cite{AMDInfo} Intern offers support for CommonJS modules but strongly recommends switching to AMD styles for your project. We chose to keep out CommonJS format because of the maturity of the evaluation project.

@@

The ability to mix assertion styles with testing interfaces provides the most diverse ways of writing tests that we've found. Some testing interfaces seems to fit better with certain assertion styles, but there's no restrictions on which can be used with which.

%- Integration with Selenium
Intern uses the WebDriver API to communicate with Selenium to drive the automated broswer testing portion of Intern. Selenium and the WebDriver API will be discussed in more detail in the next section ``Browser and UI Testing''.

%- Distinction between non-functional and functional tests
Intern's unit-test versus browser test seperation is termed, by Intern, nonfunctional versus functional testing. Nonfunctional tests are those that run without a browser while functional tests are WebDriver tests.

@@

Intern offered a one-stop shop for all of our testing needs but fell short when it came to configuring it for our Node.js server setup. If we had a more traditional web application setup with a seperate server that served normal HTML pages, Intern would have likely been our go-to tool for all of our testing needs.

@@

Tests are written as a long chain of function calls that produce an easy-to-read series of browser events. For example, the following code segment opens a browser, goes to google.com, makes some assertions, writes ``nightwatch'' in the search box, clicks the search button, and then makes a few more assertions:
\begin{lstlisting}
module.exports = {
  "Demo test Google" : function (client) {
    client
      .url("http://www.google.com")
      .waitForElementVisible("body", 1000)
      .assert.title("Google")
      .assert.visible("input[type=text]")
      .setValue("input[type=text]", "nightwatch")
      .waitForElementVisible("button[name=btnG]", 1000)
      .click("button[name=btnG]")
      .pause(1000)
      .assert.containsText("#main", "The Night Watch")
      .end();
  }
};
\end{lstlisting}
As one can see, just reading the code line by line paints a picture of exactly what is happening and what is being checked for.

@@

\paragraph{PhantomJS\cite{PhantomJS}}
The reigning king of headless browsers is PhantomJS. PhantomJS is a headless browser written using WebKit, which is what most of the web is based on. This means that running PhantomJS is nearly indistinuishable from a normal browser to any testing code.

@@

Because Jenkins comes bare and runs on the system of the devloper's choosing, it can run any project that is set up. The downside is that there is no support out-of-the-box unless the system already has the necessary compilers, interpreters, applications, and/or libraries installed.

@@

\subsubsection{Travis \cite{Travis}}
Travis is an online continuous integration framework with 29 members and 64 repositories at the time of this writing. Unlike Jenkins, Travis is all online and includes a dashboard from which the developer can monitor builds and processes. Travis has a free version which is fully-featured but requires the project to be open-source and a paid version which gives the deveoper more processing power and access to private repositories.

@@

MagnumCI offers support for Ruby, PHP, Node.JS, and Go. MagnumCI, much like Semaphore, will attempt to auto-detect commands that it should run based on the project structure and language. All settings are overridable in a yml file.

@@

Drone.io is able to connect to GitHub, BitBucket, and Google Code respositories to get projects automatically. Setup is simple, select the source of the repository (GitHub, BitBucket, or Google Code), select the repository from the list it gives once it connects, select the language of the repository, edit the default build script, and the project is ready to go.

@@

\lstinline{mocha --} specifies that the executable to be run is mocha and that the developer is done giving commandline args to istanbul, that's the \lstinline{--}

@@

Fill out the fields with the appropriate values for a given project and click ``Create Project''. Depending on what the setup is for your project, you'll see slightly varying web pages after you create your project. One thing in common, though, is the button at the bottom of the steps list that says ``Customize Build''. After following the instructions, click ``Customize Build'':
\begin{Figure}
  \centering
  \includegraphics[width=0.95\linewidth]{magnumCI_customize_build.png}
\end{Figure}
There are a number of configuration options and panes that can be accessed on the left side. Our focus was making sure the ``Build Configuration'' tab was properly set up. This involved selecing the correct branch, the correct Node.js runtime version, the correct database from the ``Resources'' area, and adding the appropriate commands in the build steps. In our case we wanted ``mongoDB'' and ``Xvfb'' for UI testing, and then \lstinline{npm install -g} in the ``Dependencies Installation'' to make sure our modules are available when we need them. Finally, we run Nightwatch using \lstinline{nightwatch -c nightwatch.json} (the nightwatch flags will be outlined in the next section) in the ``Test suite commands'' box. All of that makes our build configuration page look like this:
\begin{Figure}
  \centering
  \includegraphics[width=0.95\linewidth]{magnumCI_customize_build_filled.png}
\end{Figure}
After that setup, our project is ready to go. Anytime we commit from then on, MagnumCI will run and notify us of successful and unsuccessful builds.

@@

To run Nightwatch, navigate to the project folder and run \lstinline{nightwatch -c path\_to\_nightwatch\_config}. This will use the \lstinline{src\_folders} attribute to determine where to look for the tests, start the Selenium server, and run the tests. When debugging certain functions of even test cases, tests can be isolated with the \lstinline{-t} flag: \lstinline{nightwatch -c nightwatch.json -t folder1/test1.js}. Nightwatch offers a number of other command-line arguments that are available on their devloper guide. \cite{NightwatchJS}

@@

A more complicatied Gruntfile simply consists of more tasks. Taken one at a time, it's easy to pick apart a Gruntfile. Task names can refer to one or more commands, so the command \lstinline{grunt testMyStuff} may run one command, or may run five commands. The task names are the ones that are used as the first parameter of the \lstinline{registerTask} call.

\subsection{Workflow}
In addition to just the a list of tools and installation instructions, we'd like to propose a way to use those tools that is efficient and nearly autonomous. Our goal is to bring testing tools into use with as little resistance as possible. With a bit of effort at the outset, testing can become a crucial and enjoyable part of devlopement.

@@

For running the browser tests, we recommend using your CI tool. With some setup on your CI of choice, you can get Nightwatch running. Most CI setups have either Firefox pre-installed or Xvfb (a windowless X11 process) and all that's required is to install firefox if needed and start the selenium server using Xvfb is needed. For the CI setup, after installing all the prerequisites, run \lstinline{Xvfb :99 -ac -screen 0 1280x1024x24 &} or something more suited to the developer's liking. Make sure the \lstinline{DISPLAY} environment variable is exported, \lstinline{export DISPLAY=:99} (the numbers need to match between the xvfb call and the export). Then start your selenium server, \lstinline{java -jar path/to/selenium.jar} and it's all set. Finally, run Nightwatch and rejoice.

@@

The Author is a tool to create one's own stories. Because our tests revolved around the Author, we'll be discussing it in depth in the following section, so to avoid redundency, we'll say nothing else here.

@@

PolyXpress is meant for the general public and so there's no convuluted programming involved to create a story, it's all done through the application's Authoring tool. Screen captures of the authoring tool are in the appendix once again. The flow for creating a story is to create the Events first, the Chapters second, and finally tie it all together and create a Story. The flow is this way because the tool offers lists of existing Events in the Chapter creation page and lists of existing Chapters in the Story creation page. Doing the flow out of order or backwards would require a lot of editting of elements already created.

@@

A Story consists of most of the same things as a Chapter except that the list of Events is a list of Chapters and the user chooses whether or not they want to publish this story. If the user chooses to share the story with the world, it is placed in the marketplace, otherwise it is stored within their own list of stories and is inaccesible to anyone else.

@@

\paragraph{Sauce Labs}
Sauce Labs, the online web testing site, offered a phenonemal set of features that we did not have time to take advantage of. The ability to test web applications across multiple browsers and browser configurations without having to set all of them up is incredibly enticing.

>>>>

\subsection{Sample ToDo App}
In order to evaluate the various frameworks that we found online, we needed a small application with some functionality, but without the inherent complexity that was going to come with our evaluation application. After some searching, we decided upon a Todo application made with Express.js, Node.js, and MongoDB. \cite{ToDoAppHomePage} Here is a brief preview of the app:

@@

%%%%%%%%%%%%%%%%%%%%%%
%%% Testing Frameworks
%%%   Talk about the various frameworks
%%%%%%%%%%%%%%%%%%%%%%
\subsection{Testing Frameworks}

@@

JavaScript was chosen because it used in over 87\% of all websites. \cite{JSUsage} We also chose JavaScript because the rest of our application was written in JavaScript and we wanted to keep things as constant as possible.

@@

An important distinction that needs to be made is that in web applications there is functionality behind the scenes and there is the UI element of the web page. Unit testing frameworks are aimed at the functionality behind the scenes.

@@

This relates to Jasmine is the way that the developer writes Jasmine tests. The idea behind jasmine tests is that they read, as much as possible, like English sentences. As an example, the following is a valid Jasmine test:
\begin{lstlisting}
describe("Arithmetic Test", function () {
  it("should be able to compute the addition of two numbers", function () {
    expect(1 + 2).toEqual(3);
  });

@@

Asynchronous testing using Jasmine was a bit of a chore, but there is support built in. This support comes in the form of a three-set function progression. The first function, \lstinline!runs(function () { .... })!, runs the asynchronous code. The second function, \lstinline!waitsFor(function () { ... })!, waits for a true value from a flag or other system. Finally, the third function, another \lstinline{runs(...)}, houses the assertions to determine if the code ran properly or not. This method requires a fairly substantial amount of typing as well as complicated function chains when more than one asynchronous call is required.

\begin{lstlisting}
describe("Asynchronous specs", function() {
  var value, flag;

  it("should support async execution of test preparation and expectations", function() {
    runs(function() {
      flag = false;
      value = 0;

      setTimeout(function() {
        flag = true;
      }, 500);
    });

    waitsFor(function() {
      value++;
      return flag;
    }, "The Value should be incremented", 750);

    runs(function() {
      expect(value).toBeGreaterThan(0);
    });
  });
});
\end{lstlisting}

The above test merely sets the \lstinline{flag} to true after half of a second, thus fulfilling the \lstinline{waitsFor} function and finally the assertions are run in the final \lstinline{runs} function.

Jasmine is an interesting take on testing that we'd not see before, the BDD system in particular. We like the way assertions and tests are written in such a stylized manner. The asynchronous support is there but a bit tedious.

@@

Mocha, by default, also uses the \lstinline{describe -> it(\"should...\"} pattern to create tests. Mocha offers a variety of other test interfaces for developer's to write their test code as well as a custom, nearly unstructured variety. A few of the testing interfaces are outlined here:
\begin{lstlisting}
// BDD (default)
describe('BDD Suite', function () {
  it('should be test 1', function () {
    ...
  });
});

@@

Mocha's approach to asynchronous testing is quite a bit more straightforward than Jasmine's. In the \lstinline{it(...)} anonymous function, there is passed an additional parameter called \lstinline{done} which is then called when the asynchronous call has finished. This required us to edit the code we were testing to make all the asynchronous calls accept an additional callback, but it was a very small price to pay for extended testability. An example asynchronous test would look like this:
\begin{lstlisting}
describe("Asynch Mocha Test", function () {
  it("look like this", function (done) {
    myAsyncCall(param1, param2, function () {
      // This callback expected to run when async returns

@@

Overall Mocha offered more flexibility and better asynchronous support at the cost of additional setup. This increased flexibility came in the way of being able to select our own testing interface and assertion library so that our tests looked the way we wanted them. The cost of that was the need to find our own assertion library among the dozen that are out there. We prefer Mocha's method of asynchronous testing because it required considerably less typing on our part and was more easy to follow and read than the Jasmine chain of method calls.

\paragraph{Assertion Library of Choice: Chai.js \cite{Chaijs}}
For the assertion library we chose Chai.js.  It offers the most flexibility for writing assertions that we'd found. It provides access to an Expect API, a Should API, and a more general Assert API. The Expect API provides assertions in the form of \lstinline{expect(myVar).to.equal(10);} or \lstinline{expect(myArr).to.have.length(10);}. The Should API has assertions of the form \lstinline{myVar.should.be.a(\'number\');} or \lstinline{myArr.should.have.length(10);}. Finally, the Assert API has the more tried and true \lstinline{assert.equal(myVar, 10);} and \lstinline{assert.lengthOf(myArr, 10);}. The various APIs combined with Mocha's flexibility led to a nice developer experience that can appeal to a variety of different developers.

@@

\subsubsection{Intern\cite{InternIO}}
Intern is a hybrid unit testing and browser testing framework that aims to be an all-in-one testing framework. Intern has unit testing, browser testing, and code coverage information all built into the same tool. Intern runs on its own server which give it access to the internals of the project, but caused problems when attempting to interact with a separate server running the Node.js application. We were unable to get the browser testing portion of Intern to work because of the inability to set up cross-server communication easily and properly.

%-AMD
Intern uses Asynchronous Module Definition (AMD) form which is something we'd not seen before. Where this comes into play is merely in what used to be \lstinline{require(...)}. Instead of separately requiring modules, the entire program is wrapped in a \lstinline{define([...])} block that passes modules as parameters to an overarching function. That will make more sense after an example:
\begin{lstlisting}
// Intern
define([
    'intern!object',
    'intern/chai!assert',
    'app/hello'
], function (registerSuite, assert, hello) {
  // Test code here
});

@@

Using either style you get access to the modules outlined. AMD form offers a tighter, more straightforward way to look at module loading in addition to being better supported and having fewer gotchas. \cite{AMDInfo} Intern offers support for CommonJS modules but strongly recommends switching to AMD styles for your project. We chose to keep our CommonJS format because of the maturity of the evaluation project.

@@

The ability to mix assertion styles with testing interfaces provides a diverse way of writing tests. Some testing interfaces seems to fit better with certain assertion styles, but there's no restrictions on which can be used with which.

%- Integration with Selenium
Intern uses the WebDriver API to communicate with Selenium to drive the automated browser testing portion of Intern. Selenium and the WebDriver API will be discussed in more detail in the next section ``Browser and UI Testing''.

%- Distinction between non-functional and functional tests
Intern's unit-test versus browser test separation is termed, by Intern, nonfunctional versus functional testing. Nonfunctional tests are those that run without a browser while functional tests are WebDriver tests.

@@

Intern offered a one-stop shop for all of our testing needs but fell short when it came to configuring it for our Node.js server setup. If we had a more traditional web application setup with a separate server that served normal HTML pages, Intern would have likely been our go-to tool for all of our testing needs.

@@

Tests are written as a long chain of function calls that produce an easy-to-read series of browser events. For example, the following code segment opens a browser, goes to Google.com, makes some assertions, writes ``nightwatch'' in the search box, clicks the search button, and then makes a few more assertions:
\begin{lstlisting}
module.exports = {
  "Demo test Google" : function (client) {
    client
      .url("http://www.google.com")
      .waitForElementVisible("body", 1000)
      .assert.title("Google")
      .assert.visible("input[type=text]")
      .setValue("input[type=text]", "nightwatch")
      .waitForElementVisible("button[name=btnG]", 1000)
      .click("button[name=btnG]")
      .pause(1000)
      .assert.containsText("#main", "The Night Watch")
      .end();
  }
};
\end{lstlisting}
As one can see, just reading the code line by line paints a picture of exactly what is happening and what is being checked for.

@@

\paragraph{PhantomJS\cite{PhantomJS}}
The reigning king of headless browsers is PhantomJS. PhantomJS is a headless browser written using WebKit, which is what most of the web is based on. This means that running PhantomJS is nearly indistinguishable from a normal browser to any testing code.

@@

Because Jenkins comes bare and runs on the system of the developer's choosing, it can run any project that is set up. The downside is that there is no support out-of-the-box unless the system already has the necessary compilers, interpreters, applications, and/or libraries installed.

@@

\subsubsection{Travis \cite{Travis}}
Travis is an online continuous integration framework with 29 members and 64 repositories at the time of this writing. Unlike Jenkins, Travis is all online and includes a dashboard from which the developer can monitor builds and processes. Travis has a free version which is fully-featured but requires the project to be open-source and a paid version which gives the developer more processing power and access to private repositories.

@@

MagnumCI offers support for Ruby, PHP, Node.JS, and Go. MagnumCI, much like Semaphore, will attempt to auto-detect commands that it should run based on the project structure and language. All settings are able to be overridden in a yml file.

@@

Drone.io is able to connect to GitHub, BitBucket, and Google Code repositories to get projects automatically. Setup is simple, select the source of the repository (GitHub, BitBucket, or Google Code), select the repository from the list it gives once it connects, select the language of the repository, edit the default build script, and the project is ready to go.

@@

\lstinline{mocha --} specifies that the executable to be run is mocha and that the developer is done giving commandline arguments to istanbul, that's the \lstinline{--}

@@

Fill out the fields with the appropriate values for a given project and click ``Create Project''. Depending on what the setup is for your project, you'll see slightly varying web pages after you create your project. One thing in common, though, is the button at the bottom of the steps list that says ``Customize Build''. After following the instructions, click ``Customize Build'':
\begin{Figure}
  \centering
  \includegraphics[width=0.95\linewidth]{magnumCI_customize_build.png}
\end{Figure}
There are a number of configuration options and panes that can be accessed on the left side. Our focus was making sure the ``Build Configuration'' tab was properly set up. This involved selecting the correct branch, the correct Node.js runtime version, the correct database from the ``Resources'' area, and adding the appropriate commands in the build steps. In our case we wanted ``mongoDB'' and ``Xvfb'' for UI testing, and then \lstinline{npm install -g} in the ``Dependencies Installation'' to make sure our modules are available when we need them. Finally, we run Nightwatch using \lstinline{nightwatch -c nightwatch.json} (the nightwatch flags will be outlined in the next section) in the ``Test suite commands'' box. All of that makes our build configuration page look like this:
\begin{Figure}
  \centering
  \includegraphics[width=0.95\linewidth]{magnumCI_customize_build_filled.png}
\end{Figure}
After that setup, our project is ready to go. Anytime we commit from then on, MagnumCI will run and notify us of successful and unsuccessful builds.

@@

To run Nightwatch, navigate to the project folder and run \lstinline{nightwatch -c path\_to\_nightwatch\_config}. This will use the \lstinline{src\_folders} attribute to determine where to look for the tests, start the Selenium server, and run the tests. When debugging certain functions of even test cases, tests can be isolated with the \lstinline{-t} flag: \lstinline{nightwatch -c nightwatch.json -t folder1/test1.js}. Nightwatch offers a number of other command-line arguments that are available on their developer guide. \cite{NightwatchJS}

@@

A more complicated Gruntfile simply consists of more tasks. Taken one at a time, it's easy to pick apart a Gruntfile. Task names can refer to one or more commands, so the command \lstinline{grunt testMyStuff} may run one command, or may run five commands. The task names are the ones that are used as the first parameter of the \lstinline{registerTask} call.

\subsection{Workflow}
In addition to just the a list of tools and installation instructions, we'd like to propose a way to use those tools that is efficient and nearly autonomous. Our goal is to bring testing tools into use with as little resistance as possible. With a bit of effort at the outset, testing can become a crucial and enjoyable part of development.

@@

For running the browser tests, we recommend using your CI tool. With some setup on your CI of choice, you can get Nightwatch running. Most CI setups have either Firefox pre-installed or Xvfb (a windowless X11 process) and all that's required is to install Firefox if needed and start the selenium server using Xvfb is needed. For the CI setup, after installing all the prerequisites, run \lstinline{Xvfb :99 -ac -screen 0 1280x1024x24 &} or something more suited to the developer's liking. Make sure the \lstinline{DISPLAY} environment variable is exported, \lstinline{export DISPLAY=:99} (the numbers need to match between the xvfb call and the export). Then start your selenium server, \lstinline{java -jar path/to/selenium.jar} and it's all set. Finally, run Nightwatch and rejoice.

@@

The Author is a tool to create one's own stories. Because our tests revolved around the Author, we'll be discussing it in depth in the following section, so to avoid redundancy, we'll say nothing else here.

@@

PolyXpress is meant for the general public and so there's no convoluted programming involved to create a story, it's all done through the application's Authoring tool. Screen captures of the authoring tool are in the appendix once again. The flow for creating a story is to create the Events first, the Chapters second, and finally tie it all together and create a Story. The flow is this way because the tool offers lists of existing Events in the Chapter creation page and lists of existing Chapters in the Story creation page. Doing the flow out of order or backwards would require a lot of editing of elements already created.

@@

A Story consists of most of the same things as a Chapter except that the list of Events is a list of Chapters and the user chooses whether or not they want to publish this story. If the user chooses to share the story with the world, it is placed in the marketplace, otherwise it is stored within their own list of stories and is inaccessible to anyone else.

@@

\paragraph{Sauce Labs}
Sauce Labs, the online web testing site, offered a phenomenal set of features that we did not have time to take advantage of. The ability to test web applications across multiple browsers and browser configurations without having to set all of them up is incredibly enticing.
